Large-Scale Content-Based Matching of MIDI and Audio Files

### 2015-04-30 paper.tex
Add alignment section

\documentclass{article}
\usepackage{ismir,amsmath,cite}
\usepackage{graphicx}
\usepackage{color}
\usepackage{framed}

@@

\subsection{Audio-to-audio alignment}

>>>>

\documentclass{article}
\usepackage{ismir,amsmath,cite}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{color}
\usepackage{framed}

@@

\subsection{Synthesized MIDI-to-audio alignment}

Fuzzy metadata matching is not enough to ensure that we have correctly paired MIDI and audio files due to the following potential issues: The metadata could be incorrect, the fuzzy text match could have failed, the MIDI could be a very poor quality transcription (e.g. missing instruments or sections), and/or the MIDI and audio data could correspond to different versions of the same song.
These pitfalls necessitate a method to ensure the correctness of each MIDI/audio file pairing.
In additional, we need to align MIDI files to their corresponding audio recordings to use them as training data for our hashing model.
A common method for performing this kind of alignment is to compute the dynamic time warping (DTW) path between sequences of feature vectors \cite{turetsky2003ground, hu2003polyphonic,ewert2012towards}.
Conveniently, DTW reports a score which represents the quality of the alignment, and unsurprisingly this score tends to be very poor when nonmatching sequences are attempted to be aligned.
An overview of DTW and its application to music can be found in \cite{muller2007information}.

For our purposes, the reliability of the DTW confidence score is crucial because we will use it to decide when an audio/MIDI file pairing is valid and when an alignment can be used as training data for our hashing model.
We experimented with a variety of approaches, and converged on the following system for aligning a single MIDI/audio file pair:
First, we synthesize the MIDI data using \texttt{fluidsynth}\footnote{\texttt{http://www.fluidsynth.org}}.
We then estimate the MIDI beat locations using the MIDI file's tempo change information and the method described in \cite{raffel2014pretty_midi}.
To circumvent the common issue where the beat is tracked one-half beat out of phase, we double the BPM until it was at least 240.
Using \texttt{librosa} \cite{mcfee2014librosa}, we compute beat locations for the audio signal with the constraint that the BPM should remain close to the global MIDI tempo. 
We then compute log-amplitude beat-synchronous constant-Q transforms (CQTs) of audio and synthesized MIDI data with semitone frequency spacing and a frequency range from C3 (65.4 Hz) to C7 (1046.5 Hz), also using \texttt{librosa}.
The resulting feature matrices are then of dimensionality $N \times D$ and $M \times D$ where $N$ and $M$ are the resulting number of beats in the MIDI and audio recordings respectively and $D$ is $48$ (the number of semitones between C3 and C7).

We then use dynamic time warping to find the lowest-cost path through a full pairwise cosine similarity matrix $S \in \mathbb{R}^{N \times M}$ of the MIDI and audio CQTs.
This path can be represented as a sequence $P \in \mathbb{R}^L$ of tuples of indices from each sequence such that $P[n] = (p, q)$ implies that the $p$th MIDI beat should be aligned to the $q$th audio beat.
Traditional DTW requires that this path includes the start and end of each sequence, or equivalently that $P[1] = (1, 1)$ and $P[L] = (N, M)$.
This approach is not valid when one sequence may be a subsequence of the other, which is often true in our problem setting due to the fact that the MSD 7digital audio recordings are cropped preview clips of the entire recordings.
We therefore modify this constraint so that if $P[L] = (p, q)$ then either $gN \le p \le N$ or $gM \le q \le M$ where $g \approx 1$ is a parameter which provides a small amount of additional tolerance.
We also include the typical modification of applying an additive penalty for ``non-diagonal moves'', i.e. path entries where if $P[n] = (p, q)$ then $P[n + 1] = (p, r)$ or $P[n] = (r, q)$.
For synthesized MIDI-to-audio alignment, we used $g = .95$ and set the non-diagonal additive penality to the 90th percentile of $S$.

(Listening to alignments to find a threshold)

\subsection{Splitting the subset}`
